---
title: "**Progress Report- Group Assignment**"
author: "Elikplim Aku Setordjie, Sayesha Khanna, Abhinob Baruah and Berke Hazel Petek" 
date: "21/12/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, dev = "png", dpi = 100)
```
#### **ARTICLE AND DATA CHOSEN**
[Biocontrol of invasive pheretimoid earthworms using *Beauveria bassiana*](https://peerj.com/articles/11101/#intro)

[Data](https://dfzljdn9uc3pi.cloudfront.net/2021/11101/1/Raw_data_.xlsx)


#### **AIM OF EXPERIMENT**

To test the efficacy of *"Beauveria bassiana"* as a biocontrol agent on pheritimoid earthworms.

#### **HYPOTHESIS**

H0 : There is no significant difference between earthworms treated with *B.bassiana* and earthworms that were not treated with it.

HA : There is a significant difference between earthworms treated with *B.bassiana* and earthworms that were not treated with it.

#### **VARIABLES**

Dependent variables: Mortality, Survival 

Independent variables: Treatments, Time 

#### **TREATMENTS**

C1:Water

C2:Millet 15 grams

C3:Millet 25 grams

B. bassiana 108 conidia/mL

Mycoticized millet 15 g

Mycoticized millet 25 g	

BotaniGard® 

Some treatments were not replicated in all assays. 

#### **STEPS TO TAKE TO COMPLETE THE ASSIGNMENT**

STEP 1: Repeat analysis done in paper.

STEP 2: Re analyse the data using the most appropriate analysis in your opinion.

STEP 3: Analyse data taking time into consideration.

STEP 4: Improve upon the graphics of the paper.


```{r, echo = FALSE, include=FALSE}
#Importing data
library("readxl")      
Assay_1 <- read.csv("data/Assay 1.csv")
Assay_2 <- read.csv("data/Assay 2.csv")
Assay_3 <- read.csv("data/Assay 3.csv")
names(Assay_1) <- c("Treatments","Replication","Survivals","AdultNO",      
                   "Adult","Mortality")
names(Assay_2) <- c("Treatments","No.of.earthworms","Earthworm.weight.g","No.of.adult",
                    "Date","Group","Adults","Mortality")                
Assay_3
names(Assay_3) <- c("Treatments","Survivals","AdultsNO","Date","DayCount",
                 "Adults","Mortality","PMortality")

Assay_2 <- Assay_2[, 1:which(names(Assay_2)=="Mortality")]


```

# **STEP 1**
## **ASSAY 1**
```{r, echo = FALSE, fig.cap=cap}
cap <- paste0(
    "**Figure 1**", ": Effect of different treatments on the Mortality of Pheritimoid Earthworms")
hist(Assay_1$Mortality)   # Shape of data prior to transformation

```

```{r, echo = FALSE}
Assay_1$TMortality <- asin(sqrt(Assay_1$Mortality)) #Transforming data 

ks.test(Assay_1$TMortality, "pnorm" )      #Checking for normality
#Transformation did not make mortality data normal
```


```{r, echo = FALSE}
Anova.Assay1M <- aov(TMortality~Treatments, data = Assay_1)
ks.test(Anova.Assay1M$residuals, "pnorm")    #Checking for normality of residuals
#Transformation did not make residuals normal

Tukey1 <- TukeyHSD(Anova.Assay1M, conf.level = 0.95)
library(agricolae)
hsd <- agricolae::HSD.test(Anova.Assay1M, "Treatments")


```


```{r plot-anova, echo = FALSE, fig.cap=cap}
cap <- paste0(
    "**Figure 2**", ": Effect of different treatments on Pheritimoid earthworm mortality. ",
    " Letters indicates Tukeys HSD posthoc comparisons. ",
    " Same letter indicates non-significant differences. ")
    
plot(hsd)
```

```{r, echo=FALSE, fig.cap=cap}
cap <- paste0(
    "**Figure 3**", ":Mortality of the various treatments in Assay 1 (+/- SE) ") 

```

#Despite transforming the mortality data the article reported graphics of the untransformed data
```{r, echo = FALSE, fig.cap=cap}
data_summary <- aggregate(Mortality ~ Treatments, data = Assay_1,       # Create summary data
                          function(x) c(mean = mean(x),
                                        se = sd(x) / sqrt(length(x))))
data_summary <- data.frame(group = data_summary[ , 1], data_summary$Mortality)
data_summary                                          # Print summary data

library(ggplot2)
ggplot(Assay_1, aes(Mortality, Treatments, fill = Treatments)) +      # ggplot2 barplot with error bars
  coord_flip() +
  stat_summary(geom = "bar", fun = mean, position = "dodge") +
  stat_summary(geom = "errorbar", fun.data = mean_se, position = "dodge")
```


## **ASSAY 2**
```{r, echo = FALSE, fig.cap=cap}
cap <- paste0(
    "**Figure 4**", ": Effect of different treatments on the Mortality of Pheritimoid Earthworms") 
hist(Assay_2$Mortality) #Mortality of Assay 2 prior to transformation
```


```{r, echo=FALSE}
Assay_2$TMortality <- asin(sqrt(Assay_2$Mortality)) #Data transformation

ks.test(Assay_2$TMortality, "pnorm" )
#transformation did not make the mortality data normal

Anova.Assay2M <- aov(TMortality~Treatments, data = Assay_2)
ks.test(Anova.Assay2M$residuals, "pnorm")
#Transformation failed in making residuals normal

Tukey2 <- TukeyHSD(Anova.Assay2M, conf.level = 0.95)

library(agricolae)
hsd2 <- agricolae::HSD.test(Anova.Assay2M, "Treatments")
```


```{r, echo=FALSE,fig.cap=cap}
cap <- paste0(
    "**Figure 5**", ": Effect of different treatments on Pheritimoid earthworm mortality in Assay 2. ",
    " Letters indicates Tukeys HSD posthoc comparisons. ",
    " Same letter indicates non-significant differences. ")
    
plot(hsd2)


```

#Despite transforming the mortality data the article reported graphics of the untransformed data

```{r, echo=FALSE, fig.cap=cap}
cap <- paste0(
    "**Figure 6**", ": Mortality of earthworms in the various treatments(+/-SE)")
```

```{r, echo=FALSE, fig.cap=cap}
data_summary <- aggregate(Mortality ~ Treatments, data = Assay_2,       # Create summary data
                          function(x) c(mean = mean(x),
                                        se = sd(x) / sqrt(length(x))))
data_summary <- data.frame(group = data_summary[ , 1], data_summary$Mortality)
data_summary                                          # Print summary data

library(ggplot2)
ggplot(Assay_2, aes(Mortality, Treatments, fill = Treatments)) +      # ggplot2 barplot with error bars
  coord_flip() +
  stat_summary(geom = "bar", fun = mean, position = "dodge") +
  stat_summary(geom = "errorbar", fun.data = mean_se, position = "dodge")

```

## **ASSAY 3**
```{r, echo=FALSE, fig.cap=cap}
cap <- paste0(
    "**Figure 7**", ": Effect of different treatments on the Mortality of Pheritimoid Earthworms in Assay 3") 
hist(Assay_3$PMortality) #Mortality of Assay 3 prior to transformation
```



```{r, echo=FALSE}
Assay_3$TMortality <- asin(sqrt(Assay_3$PMortality))
ks.test(Assay_3$TMortality, "pnorm" )
#Transformation did not make the data normal.

Anova.Assay3M <- aov(TMortality~Treatments, data = Assay_3)
ks.test(Anova.Assay3M$residuals, "pnorm")
#Transformation failed in making residuals normal
```


```{r, echo=FALSE}
Tukey3 <- TukeyHSD(Anova.Assay3M, conf.level = 0.95)

library(agricolae)
hsd3 <- agricolae::HSD.test(Anova.Assay3M, "Treatments")
```


```{r, echo=FALSE, fig.cap=cap}
cap <- paste0(
    "**Figure 8**", ": Effect of different treatments on Pheritimoid earthworm mortality. ",
    " Letters indicates Tukeys HSD posthoc comparisons. ",
    " Same letter indicates non-significant differences. ")
  plot(hsd3)

```

#Despite transforming the mortality data the article reported graphics of the untransformed data

```{r, echo=FALSE,fig.cap=cap}
cap <- paste0(
    "**Figure 9**", ": Mortality of Earthworms in Various Treatments (+/-)")
```

```{r,echo=FALSE,fig.cap= cap}
data_summary <- aggregate(PMortality ~ Treatments, data = Assay_3,       # Create summary data
                          function(x) c(mean = mean(x),
                                        se = sd(x) / sqrt(length(x))))
data_summary <- data.frame(group = data_summary[ , 1], data_summary$PMortality)
data_summary                                          # Print summary data

library(ggplot2)
ggplot(Assay_3, aes(PMortality, Treatments, fill = Treatments)) +      # ggplot2 barplot with error bars
  coord_flip() +
  stat_summary(geom = "bar", fun = mean, position = "dodge") +
  stat_summary(geom = "errorbar", fun.data = mean_se, position = "dodge")


```

#### THE MORTALITY DATA IN ALL ASSAYS FAILED TO BECOME NORMALLY DISTRIBUTED AFTER THE TRANSFORMATION

#### HENCE THE MOST APPROPRAITE TEST THAT SHOULD HAVE BEEN USED TO ANALYSE THIS DATA

#### IS A NONE PARAMETRIC TEST LIKE THE KRUSKAL WALLIS TEST


# **STEP 2: KRUSKAL WALLIS ANALYSIS**
## **ASSAY 1**

```{r, echo=FALSE}
KAssay1 <- kruskal.test(Mortality ~ Treatments, data = Assay_1)
KAssay1 <- agricolae::kruskal(Assay_1$Mortality, Assay_1$Treatments)

```


```{r, echo=FALSE, fig.cap=cap}
cap <- paste0(
    "**Figure 10**", ": Effect of different treatments on the Mortality of Pheritimoid Earthworms in Assay 1") 
plot(KAssay1)
#There is no difference between results obtained with the arcsine transformed data
#and those obtained using the kruskal wallis test in Assay 1.

```

## **ASSAY 2**
```{r, echo=FALSE}
KAssay2 <- kruskal.test(Mortality ~ Treatments, data = Assay_2)
KAssay2 <- agricolae::kruskal(Assay_2$Mortality, Assay_2$Treatments) 
```


```{r, echo=FALSE, fig.cap=cap}
cap <- paste0(
    "**Figure 11**", ": Effect of different treatments on the Mortality of Pheritimoid Earthworms in Assay 2") 
plot(KAssay2)
#The Kruskal wallis test shows the differences between the various treatments
#these differences are not visible using the tukey HSD
```

## **ASSAY 3**
```{r, echo=FALSE}
KAssay3 <- kruskal.test(PMortality ~ Treatments, data = Assay_3)
KAssay3 <- agricolae::kruskal(Assay_3$PMortality, Assay_3$Treatments)

```

```{r,echo=FALSE,fig.cap=cap}
cap <- paste0(
    "**Figure 12**", ": Effect of different treatments on the Mortality of Pheritimoid Earthworms in Assay 3") 
plot(KAssay3)
# For Assay3, the tukey HSD shows more differences between the means of the
#various treatments than the kruskal wallis test.


```


```{r}
```


```{r}
```

