---
title: "**Progress Report- Group Assignment**"
author: "Elikplim Aku Setordjie, Sayesha Khanna, Abhinob Baruah and Berke Hazel Petek" 
date: "21/12/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, dev = "png", dpi = 100)
```
#### **ARTICLE AND DATA CHOSEN**
[Biocontrol of invasive pheretimoid earthworms using *Beauveria bassiana*](https://peerj.com/articles/11101/#intro)

[Data](https://dfzljdn9uc3pi.cloudfront.net/2021/11101/1/Raw_data_.xlsx)


#### **AIM OF EXPERIMENT**

To test the efficacy of *"Beauveria bassiana"* as a biocontrol agent on pheritimoid earthworms.

#### **HYPOTHESIS**

H0 : There is no significant difference between earthworms treated with *B.bassiana* and earthworms that were not treated with it.

HA : There is a significant difference between earthworms treated with *B.bassiana* and earthworms that were not treated with it.

#### **VARIABLES**

Dependent variables: Mortality, Survival 
Independent variables: Treatments, Time 

#### **STEPS TO TAKE TO COMPLETE THE ASSIGNMENT**

STEP 1: Repeat analysis done in paper.

STEP 2: Re analyse the data using the most appropriate analysis in your opinion.

STEP 3: Analyse data taking time into consideration.

STEP 4: Improve upon the graphics of the paper.


```{r, echo = FALSE, include=FALSE}
#Importing data
library("readxl")      
Assay_1 <- read.csv("data/Assay 1.csv")
Assay_2 <- read.csv("data/Assay 2.csv")
Assay_3 <- read.csv("data/Assay 3.csv")
names(Assay_1) <- c("Treatments","Replication","Survivals","AdultNO",      
                   "Adult","Mortality")
names(Assay_2) <- c("Treatments","No.of.earthworms","Earthworm.weight.g","No.of.adult",
                    "Date","Group","Adults","Mortality")                
Assay_3
names(Assay_3) <- c("Treatments","Survivals","AdultsNO","Date","DayCount",
                 "Adults","Mortality","PMortality")

Assay_2 <- Assay_2[, 1:which(names(Assay_2)=="Mortality")]


```


#ASSAY 1
```{r, echo = FALSE, fig.cap=cap}
cap <- paste0(
    "**Figure 1**", ": Effect of different treatments on the Mortality of Pheritimoid Earthworms")
hist(Assay_1$Mortality)   # Shape of data prior to transformation

```

```{r, echo = FALSE}
Assay_1$TMortality <- asin(sqrt(Assay_1$Mortality)) #Transforming data 

ks.test(Assay_1$TMortality, "pnorm" )      #Checking for normality
#Transformation did not make mortality data normal
```


```{r, echo = FALSE}
Anova.Assay1M <- aov(TMortality~Treatments, data = Assay_1)
ks.test(Anova.Assay1M$residuals, "pnorm")    #Checking for normality of residuals
#Transformation did not make residuals normal

Tukey1 <- TukeyHSD(Anova.Assay1M, conf.level = 0.95)
library(agricolae)
hsd <- agricolae::HSD.test(Anova.Assay1M, "Treatments")

```


```{r plot-anova, echo = FALSE, fig.cap=cap}
cap <- paste0(
    "**Figure 2**", ": Effect of different treatments on Pheritimoid earthworm mortality. ",
    " Letters indicates Tukeys HSD posthoc comparisons. ",
    " Same letter indicates non-significant differences. ")
    
plot(hsd)
```

#Despite transforming the mortality data the article reported graphics of the untransformed data
```{r, echo = FALSE}
dataA1 <- Assay_1 %>% select(Treatments, Mortality) 
my_sumA1 <- dataA1 %>%
  group_by(Treatments) %>%
  summarise( 
    n=n(),
  Mean.Mortality=mean(Mortality),
    sd=sd(Mortality)
  ) %>%
